\documentclass[12pt,a4paper]{article}

% ---------- PACKAGES ----------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{librebaskerville}

\renewcommand{\familydefault}{\sfdefault}
% \renewcommand{\familydefault}{\rmdefault}


% ---------- PAGE SETUP ----------
\geometry{top=1.5cm, bottom=1.5cm, left=1.6cm, right=1.6cm}
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=1.5em}

% ---------- COLOR THEME ----------
\definecolor{accent}{HTML}{03965b} % deep navy blue

% ---------- SECTION STYLE ----------
\titleformat{\section}{\large\bfseries\color{accent}}{}{0pt}{}
\titleformat{\subsection}[runin]{\bfseries\color{accent}}{}{0pt}{}[ -- ]

% ---------- LINK STYLE ----------
\hypersetup{
  colorlinks=true,
  urlcolor=black,   % links stay black
  linkcolor=black,
  citecolor=black
}

% ---------- HEADER ----------
\begin{document}
\pagestyle{empty}
% --- HEADER BLOCK ---
\noindent
\begin{minipage}[t]{0.65\textwidth}
  {\LARGE \textbf{Koushik Ruidas}}\\
  \textbf{Solution Architect -- Cloud \& Distributed Systems}\\[4pt]
  Email: \href{mailto:koushikruidas@gmail.com}{koushikruidas@gmail.com}\\
  Mobile: +91 9002662116\\
\end{minipage}%
\begin{minipage}[t]{0.35\textwidth}
  \raggedleft
  \begin{tabular}{@{}r l@{}}
    \textbf{GitHub:} & \href{https://github.com/koushikruidas}{\textcolor{blue}{//koushikruidas}} \\
    \textbf{LinkedIn:} & \href{https://www.linkedin.com/in/koushik-ruidas-1a73b1108/}{\textcolor{blue}{//in/koushik-ruidas}} \\
  \end{tabular}
\end{minipage}

\vspace{6pt}
\hrule
\vspace{10pt}

% ---------- EDUCATION ----------
\section*{Education}
\textbf{Indian Institute of Engineering Science and Technology, Shibpur}\\[2pt]
\textit{Bachelor of Engineering (B.E.) in Information Technology} \hfill 2012 -- 2016\\
\\
\textbf{A Zone Boys High School, Durgapur}\\[2pt]
\textit{West Bengal Board of Higher Secondary Examination (Class XII)} \hfill 2009 -- 2011\\
\\
\textbf{B Zone Boys High School, Durgapur}\\[2pt]
\textit{West Bengal Board of Secondary Examination (Class X)} \hfill 2008 -- 2009


% ---------- SKILLS ----------
\section*{Skills}
\textbf{Strengths:} Cloud Architecture, Microservices, Security, DevOps, Leadership\\
\textbf{Proficient in:} Java, Spring Boot, Spring Cloud, Spring Security, Docker, AWS, Kafka, SQL

% ---------- EXPERIENCE ----------
\section*{Industry Experience}

\textbf{Cognizant} — \textbf{\textit{Engineering Manager}}
 \hfill Kolkata, India (2023 -- Present)\\
Technologies: AWS, Microservices, Spring Boot, OAuth2, Docker
\begin{itemize}
  \item Leading migration of a mainframe system to a Java Spring Boot--Angular microservices platform (FIS client).
  \item Designed scalable cloud-native architecture and CI/CD pipelines ensuring deployment automation.
  \item Managing cross-functional backend, frontend, and BA teams to deliver enterprise-grade systems.
  \item Driving client communication and stakeholder management through regular demos and reports.
  \item Mentoring developers on distributed system design, performance tuning, and best practices.
  % \item Contributed to project estimation, requirement analysis, and solution documentation.
\end{itemize}

\textbf{PwC} — \textbf{\textit{Senior Associate}} \hfill Kolkata, India (2021 -- 2022)\\
Technologies: Spring Boot, JPA, Hibernate, Eureka, Hystrix, JWT
\begin{itemize}
  \item Led 6-member team to deliver MDM module for the SAMAST power scheduling system.
  \item Built secure microservices ecosystem with API Gateway, JWT auth, and fault tolerance using Hystrix.
  \item Designed and optimized meter data ingestion and energy analytics reporting modules.
  \item Collaborated with business teams for requirement clarification and functional testing.
\end{itemize}

\textbf{Accenture} — \textbf{\textit{Senior Software Engineer}} \hfill Bangalore, India (2016 -- 2021)\\
Technologies: Java, Spring Boot, AWS, Kafka, FIX Protocol
\begin{itemize}
  \item Developed FIX client integrating ICE exchange deals into Shell's record systems.
  \item Built real-time deal streaming pipelines using Kafka for low-latency updates.
  \item Supported multiple internal tools (MAST, MPS, CCM) for monitoring, message processing, and contract confirmation.
\end{itemize}

% ---------- PROJECTS ----------
% \section*{Projects}
% \textbf{LogPulse (Open Source)} — Real-time log analysis platform with Kafka and ELK.\\
% \textbf{CloudDeployX} — Infrastructure-as-code deployment framework using Terraform + AWS Lambda.

% % ---------- PUBLICATIONS ----------
% \section*{Publications / Research}
% System Call Interception for Serverless Isolation – ACM SIGCOMM Demos \& Posters 2020\\
% Federated Adaptive Bitrate Live Streaming – ACM SIGCOMM NAI 2020

% % ---------- CERTIFICATIONS ----------
% \section*{Certifications}
% AWS Certified Solutions Architect – Associate (2023)\\
% Certified Kubernetes Administrator (2022)

% % ---------- VOLUNTEERING ----------
% \section*{Conferences / Volunteering}
% COMSNETS 2020 Volunteer, MobiCom 2019 Volunteer, AIMLSystems 2021 Web Chair

% ---------- FOOTER ----------
% \vspace{8pt}
% \hrule
% \vspace{6pt}
% \centering
% Page \thepage\ of \pageref{LastPage}

\end{document}
